% !Mode:: "TeX:UTF-8"

\myabstract{
中文摘要一般为300~400字，简要介绍毕业设计（论文）的研究目的、方法、结果和结论，语言力求精炼。英文摘要应与中文摘要相对应。中英文摘要均要有关键词，一般为3\~8个，中英文摘要要相互对应。

中文摘要。“摘要”两字之间空一个全角空格或两个半角空格，字体为宋体二号字加粗，居中显示，摘要内容采用正文样式。中文关键词与摘要内容间隔一行，无缩进左对齐书写。“关键词：”采用宋体四号字加粗，关键词内容采用正文样式，且换行不缩进。关键词之间用逗号分隔。

英文摘要。此部分皆为Times New Roman字体。“ABSTRACT”为二号字加粗，居中显示。英文摘要内容采用正文样式。英文关键词与英文摘要内容间隔一行，无缩进左对齐书写。“KEY WORDS:”为四号字加粗，英文关键词采用正文样式，且换行不缩进，关键词之间用逗号分隔，词义和中文关键词相同。“ABSTRACT”和“KEY WORDS”一律用大写字母，每个关键词的首字母要大写。
}

\mykeywords{关键词1，关键词2，关键词3，关键词4，关键词5，三至五个关键词（宋体 小四号 不加粗，分号隔开，如果不换页，与摘要空一行）
}

\myeabstract{
Chinese Abstract. "Abstract" is written in bold with size 2, and centered in boldface, using Song typeface. The abstract content is in regular text style. There should be a space between "Abstract" and the content. Chinese keywords are separated from the abstract content by one line, left-aligned with no indentation. "Keywords:" is in bold with size 4, and the keywords are in regular text style, separated by commas without indentation.

English Abstract. This section is all in Times New Roman font. "ABSTRACT" is written in bold with size 2, centered in boldface. The abstract content is in regular text style. English keywords are separated from the abstract content by one line, left-aligned with no indentation. "KEY WORDS:" is in bold with size 4, and the keywords are in regular text style, separated by commas without indentation, and the meanings should correspond to the Chinese keywords. "ABSTRACT" and "KEY WORDS" are all capitalized. The first letter of each keyword should be capitalized.
}

\myekeywords{Heat transfer, Mechanics, Combustion, Engine, Analysis}

\makeabstract